Fastqc Analysis of raw reads

### 2019-05-05 notebooks/article_notebook2.Rmd
added gyrB substitutions

```{r include=FALSE}
# Libraries
library(dplyr)
library(tidyr)
library(kableExtra)
```

```{r Import data, include = FALSE}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-415-2-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S"
  )

@@

>>>>

```{r message = FALSE, warning=FALSE}
# Libraries
library(dplyr)
library(tidyr)
library(kableExtra)
```

```{r Import data, message=FALSE, warning=FALSE}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-415-2-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S"
  )

@@

# Substitutions in GyrB outside QRDR
```{r}
mut_filtered %>%
  filter(gene == "gyrB") %>%
  group_by(mut) %>%
  count() %>%
  filter(mut != "0") %>%
  dplyr::rename("AA Substitution" = mut) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 2019-05-05 notebooks/assembly_metrics.Rmd

```{r, include = FALSE}
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, scales)

"%not_in%" <- Negate("%in%")

@@

# Import files and clean data
```{r}
files <- file_names(path)

@@

  # Create encoded Base64 datastream 
  encode_data <- function(x){
    write.csv2(x, "./file.csv")
    enc= sprintf('data:text/csv;base64,%s', openssl::base64_encode(paste0(readLines("./file.csv"), collapse="\n")) )
    unlink("./file.csv")
    return(enc)
  }

>>>>

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(scales)
```

```{r, include = FALSE}
"%not_in%" <- Negate("%in%")

@@

```{r, message=FALSE, warning=FALSE}
files <- file_names(path)

@@

  # Create encoded Base64 datastream 
  encode_data <- function(x){
    write.csv2(x, "./file.csv")
    enc= sprintf('data:text/csv;base64,%s',
                 openssl::base64_encode(
                   paste0(
                     readLines("./file.csv"),
                     collapse="\n")
                   )
                 )
    unlink("./file.csv")
    return(enc)
  }

### 2019-05-05 notebooks/fastqc_analysis.Rmd

---
title: "Fastqc Analysis of Raw Reads"
author: "Håkon Kaspersen"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
    html_document:
      code_folding: hide
      df_print: paged
      highlight: kate
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 3
      toc_float:
        collapsed: yes
    pdf_document:
      toc: yes
      toc_depth: '3'
---

# Dependencies
This analysis depends on the following packages:

- fastqcr

- dplyr

- ggplot2

- tidyr

- viridis

- ggsci

- scales

```{r, include = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(fastqcr,dplyr,ggplot2,tidyr,viridis,ggsci,scales)
```

@@

# Functions
```{r}
# Function that lists all the file names in the input folder
file_names <- function(filepath, folder) {
  files <- list.files(path = paste0(filepath, "/", folder), pattern = "_fastqc.zip")
  return(files)
}

>>>>

---
title: "Fastqc Analysis of raw reads"
author: "Håkon Kaspersen"
date: '`r format(Sys.time(), "%d.%m.%Y")`'
output:
    html_document:
      code_folding: hide
      df_print: paged
      highlight: kate
      number_sections: yes
      theme: flatly
      toc: yes
      toc_depth: 3
      toc_float:
        collapsed: yes
    pdf_document:
      toc: yes
      toc_depth: '3'
---

```{r, message=FALSE, warning=FALSE}
library(fastqcr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(viridis)
library(ggsci)
library(scales)
```

@@

```{r}
# Function that lists all the file names in the input folder
file_names <- function(filepath, folder) {
  files <- list.files(path = paste0(filepath, "/", folder), pattern = "_fastqc.zip")
  return(files)
}
